How to use replication assignments for teaching integrity in empirical archaeology

### 2019-08-16 README.Rmd
tweaks to readme
add Ryan's ORCID
add more orcids :)

> Marwick, B. [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531), L. Wang [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9060-2125), R. Robinson, H. Loiselle (2019). _`r Title`_. Submitted to _Advances in Archaeological Practice_ <https://doi.org/10.17605/OSF.IO/DBSW9>

@@

### Overview of contents

@@

### How to run in your broswer or download and run locally

>>>>

> Marwick, B. [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531), L. Wang [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-9060-2125), R. Robinson [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-8029-937X), H. Loiselle [![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0002-6197-4752) (2019). _`r Title`_. Submitted to _Advances in Archaeological Practice_ <https://doi.org/10.17605/OSF.IO/DBSW9>

@@

@@

## How to run in your broswer or download and run locally
